\\textbf{\\textsc{Supplementary Material} \\linebreak \\linebreak Not just for programmers: How GitHub can accelerate collaborative and reproducible research in ecology and evolution \\linebreak \\linebreak Methods to create \\textsl{the scatterblob} figure}

### 2023-02-23 R/Supp_Info_1.Rmd
Returns the italics to the sentence that needs attention. Oops!

Each author attributed a value ranging from 1 to 10 to their perceived degree of collaboration for a use case, with one representing a use case that offer very low advantages in terms of collaboration, while ten classified that use case as highly advantageous in terms of collaboration.

>>>>

_Each author attributed a value ranging from 1 to 10 to their perceived degree of collaboration for a use case, with one representing a use case that offer very low advantages in terms of collaboration, while ten classified that use case as highly advantageous in terms of collaboration._
